---
title: "Masjids in Brunei"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Masjids in Brunei}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette introduces the `masjid` dataset included in the `{bruneimap}` package, which provides spatial data for masjids (mosques) across Brunei. 
The dataset includes essential information such as the name, geographic coordinates (latitude and longitude), and district of each masjid.

```{r setup}
library(tidyverse)
library(bruneimap)
library(sf)
```

```{r}
glimpse(masjid)
```

We can visualise the locations of masjids across Brunei 
Below is an example where the masjids are overlaid on Brunei’s kampong boundaries:

```{r}
ggplot() +
  geom_sf(data = kpg_sf, fill = NA) +
  geom_point(data = masjid, aes(latitude, longitude), inherit.aes = FALSE) +
  theme_bw()
```

<!-- To visualise the intensity of masjids based on their locations, a density heatmap is a good approach.  -->
<!-- This can be done using `geom_density_2d` or `geom_density_2d_filled` in ggplot2.  -->

<!-- ```{r} -->
<!-- library(tidyverse) -->
<!-- library(bruneimap) -->

<!-- # Calculate bounding box of Brunei from the kampong boundaries -->
<!-- brunei_bbox <- st_bbox(kpg_sf) -->

<!-- # Crop the masjid data to the bounding box of Brunei -->
<!-- masjid_cropped <- masjid %>% -->
<!--   filter( -->
<!--     latitude >= brunei_bbox["ymin"] & latitude <= brunei_bbox["ymax"], -->
<!--     longitude >= brunei_bbox["xmin"] & longitude <= brunei_bbox["xmax"] -->
<!--   ) -->

<!-- # Visualize intensity of masjids within Brunei's boundaries -->
<!-- ggplot() + -->
<!--   # Add kampong boundaries -->
<!--   geom_sf(data = kpg_sf, fill = NA, color = "gray70") + -->
<!--   # Add density visualization of cropped masjid locations -->
<!--   geom_density_2d_filled(data = masjid_cropped, aes(x = latitude, y = longitude), alpha = 0.7) + -->
<!--   # Add masjid locations as points for reference -->
<!--   geom_point(data = masjid_cropped, aes(x = latitude, y = longitude), color = "red", size = 1) + -->
<!--   # Customize map appearance -->
<!--   scale_fill_viridis_c(option = "C") + -->
<!--   theme_minimal() + -->
<!--   labs( -->
<!--     title = "Intensity of Masjid Locations in Brunei", -->
<!--     x = "Latitude", -->
<!--     y = "Longitude", -->
<!--     fill = "Intensity" -->
<!--   ) -->

<!-- ``` -->

